Confirmation of \srcfull{} as a long period radio transient

### 2025-05-17 paper/main.tex
Synched paper with overleaf. Also updated lpt comparison plot script slightly. WIP

We conclude, therefore, that \src{} is intermittent and that the active periods have durations on the order of months.
Even when the source is ``on'', it can apparently change in brightness by an order of magnitude or more (at a given frequency) in different months.
This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was observed over a three-month period, but has not been seen again \citep{2022Natur.601..526H}.
The reappearance of \src{} after so many months suggests the possibility that other known intermittent LPTs (like GLEAM-X J162759.5$-$523504.3 and GCRT J1745$-$3009) may eventually do likewise.

@@

\src{} shares several properties similar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars.
\src{}'s period of ${\sim}1.16\,$hours is marginally shorter than the minimum known orbital period of $1.3\,$hours \citep{schwope2025polarcatcatalogpolarslowaccretion}, making it a good candidate for testing the suggestion put forward by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent AM CVns and CVs respectively.

@@

>>>>

We conclude, therefore, that \src{} is intermittent with active periods lasting on the order of months.
The given set of observations, spanning from 2023 to 2024, may represent two or three different activity windows.
This is reminiscent of the behaviour of GLEAM-X J162759.5$-$523504.3, which was ``on'' in January 2020, ``off'' in Feburary, and ``on'' again in March \citep{2022Natur.601..526H}.
The reappearance of \src{} after so many months suggests the possibility that other known intermittent LPTs (like GLEAM-X J162759.5$-$523504.3 and GCRT J1745$-$3009) may eventually do likewise.
% TODO: Note activity-window similarities to other GCRTs

@@

\src{}'s period and duty cycle are not dissimilar to ILT J1101+5521 and GLEAM-X J0704$-$37, which are confirmed polars (Fig. \ref{fig:lpt_comparison}), suggesting the possibility that \src{}, too, is a WD-MD polar system.
However, its period of ${\sim}1.16\,$hours would make it shorter than the minimum known orbital period of $1.3\,$hours for confirmed polars \citep{schwope2025polarcatcatalogpolarslowaccretion}.
This makes it a good candidate for testing the suggestion advanced by \citet{2025arXiv250103315R} that ``short LPTs'' ($P \lesssim 78\,$mins) and ``long LPTs'' ($P \gtrsim 78\,$mins) represent different classes of systems (AM CVns and CVs, respectively).
\begin{figure*}[th]
    \centering
    \includegraphics[width=0.98\linewidth]{lpt_comparison.pdf}
    \caption{Duty cycle vs radio pulse period for various classes of radio emitters. (TODO: add AR Sco and J1912.) The duty cycles are derived from the reported pulse widths for LPTs, which are compared to the range of the fitted, unscattered pulse widths of \src{} at 10\% of the peak.}
    \label{fig:enter-label}
\end{figure*}

@@

%%%%% Other things to possibly discuss:
% - Qu & Zhang #2: https://ui.adsabs.harvard.edu/abs/2025ApJ...981...34Q/abstract
% - Gaia22ayj: https://ui.adsabs.harvard.edu/abs/2025PASP..137b4202R/abstract
% - Trying to find a number for the radio duty cycle of AR Sco
%   - This one's about the pair-wise alternation of (optical?) pulse brightnesses, and an interpretation involving precession: https://ui.adsabs.harvard.edu/abs/2023ApJ...958L..22G/abstract
%   - Fancy AR Sco modelling. Magnetic mirror models are mentioned in the abstract? https://ui.adsabs.harvard.edu/abs/2025arXiv250508567D/abstract
% - https://ui.adsabs.harvard.edu/abs/2022Ap%26SS.367..108K/abstract
% - Suggestion that J1627 is a WD pulsar: https://ui.adsabs.harvard.edu/abs/2022Ap%26SS.367..108K/abstract
